Circular Regression Trees and Forests with an Application to Probabilistic Wind Direction Forecasting

### 2020-01-02 pkg/circtree/inst/wind_paper/draft/draft.Rnw
Update url of georg
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2945 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 03adb4d7b24dda3bedff0c29144fd91df8dc3114

  Georg~J.~Mayr\\
  Universit\"at Innsbruck \\
  Department of Atmospheric and Cryospheric Science \\
  Faculty of Geo- and Atmospheric Sciences \\
  Innrain~52f \\
  6020 Innsbruck, Austria \\
  E-mail: \email{Georg.Mayr@uibk.ac.at} \\
  URL: \url{http://acinn.uibk.ac.at/persons/georg_mayr}\\

>>>>

  Georg~J.~Mayr\\
  Universit\"at Innsbruck \\
  Department of Atmospheric and Cryospheric Science \\
  Faculty of Geo- and Atmospheric Sciences \\
  Innrain~52f \\
  6020 Innsbruck, Austria \\
  E-mail: \email{Georg.Mayr@uibk.ac.at} \\
  URL: \url{https://www.uibk.ac.at/acinn/people/georg-mayr}\\
